---
title: "reading_data_from_the_web"
author: "Tiffany Xi"
date: "10/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Load some packages.

```{r}
library(rvest)
library(httr)
```
 
### Scrape a table

First get the HTML

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml = read_html(url)
#got html code from the internet and loaded into r
drug_use_xml
```

Get the tables from the HTML

html_nodes(css = "table")---pull out all of the html objects that labeled "table"
```{r}
drug_use_xml %>%
  html_nodes(css = "table") %>% 
  class
```

.[[1]]---give me the first object of the list--.[[2]] get the second table
slice(-1)---take out the first row of the df---filter is better!

```{r}
drug_use_xml %>%
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table() %>% 
  slice(-1) %>% 
  as_tibble()
```

```{r}
table_marj = (drug_use_xml %>% html_nodes(css = "table"))[[1]] %>%
  html_table() %>%
  .[-1,] %>% 
  as_tibble()
```

This dataframe is very untidy!


### Cost of living

```{r}
nyc_cost = read_html("https://www.bestplaces.net/cost_of_living/city/new_york/new_york") %>%
  html_nodes(css = "table") %>%
  .[[1]] %>%
  html_table(header = TRUE)
```


### Harry Potter

Let's get some Potter data!

```{r}
hpsaga_html = read_html("https://www.imdb.com/list/ls000630791/")
```


```{r}
title_vec = hpsaga_html %>%
  html_nodes(css = ".lister-item-header a") %>%
  html_text()

gross_rev_vec = hpsaga_html %>%
  html_nodes(".text-muted .ghost~ .text-muted+ span") %>%
  html_text()

runtime_vec = hpsaga_html %>%
  html_nodes(".runtime") %>%
  html_text()

hpsaga_df = tibble(
  title = title_vec,
  rev = gross_rev_vec,
  runtime = runtime_vec
)
```


### Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

## APIs

Get the water data

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
  content("parsed")
```

As JSON

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.json") %>% 
  content("text") %>% 
  jsonlite::fromJSON() %>% 
  as_tibble()
```

BRFSS -- not run because it takes too long.

```{r}
brfss_smart2010 = 
  GET("https://data.cdc.gov/api/views/acme-vg9e/rows.csv?accessType=DOWNLOAD") %>% 
  content("parsed")

```


```{r}
poke = GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()
poke$name
poke$height
poke$abilities
```

